Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-10 hpmoon-asoco.tex
Clarifying how selection to migrate is done
Address some comments

\textcolor{blue}{This migration
  is performed asynchronously, as it has the advantage of being a
  non-blocking operation \cite{TalbiUnified2018}. The individual
  chosen to migrate is selected from the subpopulation using Binary
  Tournament, as proposed in previous papers
  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island
  starts the migration step, the migrated individual is sent to
  another randomly selected island. This makes it possible a
  dissemination of the modified parts of the individuals among the
  whole set of islands, thus avoiding a specific synchronization step
  to compose solutions obtained by different islands, as occurs other
  works \cite{Dorronsoro13superlinear}.}

@@

%ZDT1
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt1_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt1_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt1_2048.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt1_2048}
\end{figure}

%ZDT2
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt2_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt2_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt2_2048.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt2_2048}
\end{figure}

%ZDT3
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt3_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt3_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt3_2048.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent of running $D$ and $O$ respectively. }}
\label{fig:plot_zdt3_2048}
\end{figure}

@@

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one arbitrary sample run of each combination. These figures allow to visualize the effect of the different chromosome sizes and number of islands in each different benchmark. The first one, ZDT1, has a convex Pareto-optimal front. Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the generated PFs depends on the chromosome size. Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown on average in Table \ref{tab:results512}. Nevertheless, if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear. It can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows. However, with $A$, the area covered by the PF is still larger.}

>>>>

\textcolor{blue}{This migration
  is performed asynchronously, as it has the advantage of being a
  non-blocking operation \cite{TalbiUnified2018}. The individual
  chosen to migrate is selected from the subpopulation using Binary
  Tournament from a randomly selected couple, as proposed in previous papers
  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island
  starts the migration step, the migrated individual is sent to
  another randomly selected island. This makes it possible a
  dissemination of the modified parts of the individuals among the
  whole set of islands, thus avoiding a specific synchronization step
  to compose solutions obtained by different islands, as occurs other
  works \cite{Dorronsoro13superlinear}.}

@@

%ZDT1
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt1_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively. }}
\label{fig:plot_zdt1_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt1_2048.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT1 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively. }}
\label{fig:plot_zdt1_2048}
\end{figure}

%ZDT2
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt2_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively. }}
\label{fig:plot_zdt2_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt2_2048.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT2 problem with a chromosome size ($L$) of 2048 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively. }}
\label{fig:plot_zdt2_2048}
\end{figure}

%ZDT3
\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt3_512.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the ZDT3 problem with a chromosome size ($L$) of 512 for each combination of number of islands ($P$) and method: baseline ($B$), disjoint ($D$), overlapped ($O$) and automatic overlapped ($A$). Results for 8 and 16 islands of $A$ are equivalent to running $D$ and $O$ respectively. }}
\label{fig:plot_zdt3_512}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=12cm]{plot_zdt3_2048.png}
\caption{\textcolor{blue}{PFs obtained in one arbitrary run for the
    ZDT3 problem with a chromosome size ($L$) of 2048 for each
    combination of number of islands ($P$) and method: baseline ($B$),
    disjoint ($D$), overlapped ($O$) and automatic overlapped
    ($A$). Results for 8 and 16 islands of $A$ are equivalent to
    running $D$ and $O$ respectively. }}
% It would be interesting to comment something about what is the key
% thing here and what's good about it. Without an a priori idea, I
% wouldn't know which one looks the best - JJ
\label{fig:plot_zdt3_2048}
\end{figure}

@@

 %%%%%% FERGU: WARNING, THIS SECTION IS STILL SHIT
 % By now, maybe it should not be (or you should delete this
 % comment) - JJ
%ZDT1 
\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one arbitrary sample run of each combination. These figures allow to visualize the effect of the different chromosome sizes and number of islands in each different benchmark. The first one, ZDT1, has a convex Pareto-optimal front. Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the generated PFs depends on the chromosome size. Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown on average in Table \ref{tab:results512}. Nevertheless, if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear. It can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows. However, with $A$, the area covered by the PF is still larger.}
